---
title: "GIS-Deliverable"
author: "Catharina Clark"
date: "2025-03-04"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Libraries

```{r libraries}

library(httr)
library(sf) 
library(ggplot2)
library(ggspatial)
library(leaflet)
library(dplyr)
library(rinat)

```


## Striped Mouse (Rhabdomys pumilio) Data Retrievals from iNat

```{r striped mouse data}

data_striped_mouse <- get_inat_obs(
  taxon_name = "Rhabdomys pumilio",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_striped_mouse)
names(data_striped_mouse)


```


## Vlei Rat (Elephantulus edwardii) Data Retrievals from iNat

```{r vlei rat data}

data_vlei_rat <- get_inat_obs(
  taxon_name = "Elephantulus edwardii",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_vlei_rat)
names(data_vlei_rat)


```


## Cape Gerbil (Crocidura cyanea) Data Retrievals from iNat

```{r cape gerbil data}

data_cape_gerbil <- get_inat_obs(
  taxon_name = "Crocidura cyanea",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_vlei_rat)
names(data_vlei_rat)


```


## Pygmy mouse (Mus minutoides) Data Retrievals from iNat

```{r pygmy mouse data}

data_pygmy_mouse <- get_inat_obs(
  taxon_name = "Mus minutoides",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_vlei_rat)
names(data_vlei_rat)


```


## Grey musk shrew (Micaelamys namaquensis) Data Retrievals from iNat

```{r shrew data}

data_grey_musk_shrew <- get_inat_obs(
  taxon_name = "Micaelamys namaquensis",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_vlei_rat)
names(data_vlei_rat)


```


## Cape rock sengi (Otomys irroratus) Data Retrievals from iNat

```{r rock sengi data}

data_cape_rock_sengi <- get_inat_obs(
  taxon_name = "Otomys irroratus",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_vlei_rat)
names(data_vlei_rat)


```


## Namaqua rock mouse (Gerbilliscus afra) Data Retrievals from iNat

```{r rock mouse data}

data_namaqua_rock_mouse <- get_inat_obs(
  taxon_name = "Gerbilliscus afra",
  quality = "research", 
  geo = TRUE, 
  place_id = 113055, 
  maxresults = 1000     
)

head(data_vlei_rat)
names(data_vlei_rat)


```


## Making into Map

```{r}

small_mammals_map <- leaflet() %>%
  addTiles() %>%  
  
  addCircleMarkers(data = data_vlei_rat, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "blue", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%
  
  addCircleMarkers(data = data_striped_mouse, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "green", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%
  
  addCircleMarkers(data = data_pygmy_mouse, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "red", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%
  
  addCircleMarkers(data = data_cape_gerbil, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "purple", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%
  
  addCircleMarkers(data = data_grey_musk_shrew, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "grey", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%
  
  addCircleMarkers(data = data_cape_rock_sengi, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "orange", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%
  
  addCircleMarkers(data = data_namaqua_rock_mouse, 
                   lng = ~longitude, lat = ~latitude, 
                   popup = ~paste("Common Name:", common_name, "<br>Species:", scientific_name, 
                                  "<br>Observation Date:", observed_on),
                   color = "black", radius = 5, stroke = FALSE, fillOpacity = 0.7) %>%

  addLegend("bottomright", 
            colors = c("blue", "green", "red", "purple", "grey", "orange", "black"), 
            labels = c("Vlei rat", "Striped mouse", "Pygmy mouse", "Cape gerbil", "Grey musk shrew", "Cape rock sengi", "Namaqua rock mouse"),
            title = "Species")

small_mammals_map
```

